Functional Pearl --- Programming with \\ Negative, Fractional, Square Root, and Imaginary Types

### 2012-02-23 dual.tex
intro ideas

>>>>

The world of computation we are describing has:
\begin{itemize}
\item suppliers, 
\item consumers, and
\item bi-directional transformations
\end{itemize}
This is the same world described by the papers on the duality of computation
but that work only scratched the surface! We have the following features:
\begin{itemize}
\item we can start from the supplier and push the values towards the
  consumer (call-by-value in the duality of computation papers)
\item we can start from the consumer and pull the values from the suppliers
  (call-by-name in the duality of computation papers)
\item we can combine the pushing and pulling and values using eta/epsilon for
  sum types; these allow us to at any point in the middle of the computation
  create out of nothing a value to send to the consumers and a demand to send
  to the suppliers.
\item we can break a big data structure into fragments described by
  fractional types; the suppliers and consumers can produce and consume the
  pieces completely independently of each other. Eventually the pieces will
  fit together at the consumer to produce the desired output.
\item we can break a bi-directional transformation into pieces using square
  roots
\item we can take into account that values have phase (complex numbers),
  i.e., it is not that they flow towards the consumer or just towards the
  suppliers; they can be flowing in direction that ``30 degrees'' towards the
  consumer for example.
\end{itemize}
So it is all about breaking dependencies in some sense to allow for maximum
autonomy (parallelism) of subcomputations. It is probably the case that to
make full use of square root types and imaginary types, we have to move to a
vector space. If that's the case, we should probably leave this stuff out and
focus on negative and fractional types and only have a short discussion of
the polynomials restricted to seven trees in one and similar issues.
